### 2021-04-08 papers/SYRCoSE/intro.tex
SYRCoSE: minor

In this work in progress report we sketch 
the common design principles behind our library
and give a concrete example of its usage  
by developing a formal mechanised semantics of simple 
register machine with shared memory.

>>>>

In this work-in-progress report we sketch 
the common design principles behind our library
and give a concrete example of its usage  
by developing a formal mechanised semantics of simple 
register machine with shared memory.
